Reinforcement Learning for Options on Target Volatility Funds

### 2021-05-07 tex/targetvol.tex
New Market data condition
creation of a new market with two equities: one with a smile and the
other with a displaced diffusion (equal repo). Then little change in the
 baseline run.py: bang bang solution
Correct Values for BS price and Baseline Price+Fix import error of pyGem

\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%\usepackage[outer=5cm, marginparwidth=4.5cm]{geometry}
%\usepackage{marginnote}
\usepackage{amssymb,amsmath,amsthm,latexsym,amsfonts,amscd,dsfont,enumerate,bbm,mathabx}
\usepackage{graphicx,tikz}
\usepackage{draftwatermark}
% \usepackage{listings}
% \usepackage{booktabs}
\usepackage{mathtools}
% \usepackage[gen]{eurosym}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
\usepackage{soul}

@@

\newcommand{\tr}[1]{{#1}^{\intercal}} %transpose
\let\oldnorm\norm   % <-- Store original \norm as \oldnorm
\let\norm\undefined % <-- "Undefine" \norm
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

@@

\title{Optimal Strategies for Target Volatility Contracts}

\author{
Roberto Daluiso\thanks{Banca IMI Milan, roberto.daluiso@bancaimi.com}
\and 
  Andrea Pallavicini\thanks{Imperial College London and Banca IMI Milan, a.pallavicini@imperial.ac.uk} 
\and
  Emanuele Nastasi\thanks{Exprivia, emanuele.nastasi@exprivia.com}
  \and Stefano Polo \thanks{Intesa Sanpaolo Milan, stefano.polo@intesasanpaolo.com}% indicates same as 2nd thanks
}

\date{} % leave empty
\begin{document} % goes here

@@

\begin{abstract}
...
\end{abstract}

\smallskip
\noindent
\textbf{JEL classification codes:} C63, G13.\\
\textbf{AMS classification codes:} 65C05, 91G20, 91G60.\\
\textbf{Keywords:} Asset Allocation, Target Volatility, Funding Costs, Hedging Cost, Reinforcement Learning, Proximal policy optimization. 
\clearpage
\tableofcontents
 % \vspace{\fill\footnotesize \noindent The opinions here expressed are solely those of the authors and do not represent in any way those of their employers.}
\clearpage
\pagestyle{fancy}  
\section{Introduction}
In the recent years portfolio managers are exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such environment is given by target volatility strategies (TVSs) (also known as constant volatility targeting) which are able to preserve the portfolio at a predetermined level of volatility. A TVS is  a  portfolio  of  risky  assets  (typically  equities)  and  a  risk-free  asset dynamically re-balanced with the aim of maintaining the overall portfolio volatility level closed to some target value. This products were initially offered in the Asian markets, see for instance the reports of \cite{Chew} and \cite{XUE} which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \cite{Morrison}.

In literature TVSs are tested to investigate their performances in term of realized returns, see for instance \cite{Hocquard28} and \cite{PERCHET}, and the soundness of the volatility targeting algorithm, as described in \cite{Kim}. Moreover, in pricing literature derivative contracts on TVS are studied, see in particular \cite{Di_Graziano}, \cite{Grasselli}, and \cite{Albeverio}.

@@

Valuation adjustments (XVAs) is a topic widely discussed in the literature. We refer to \cite{Brigo} for a discussion. Since fund managers allocating TVS usually rely on Equity assets, here we use the results of \cite{Gabrielli} which  analyze the valuation adjustments for equity products. We can write
\begin{equation}
    \psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du,
\label{eq:XVA_equity}\end{equation}
where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

@@

Yet, the strategy priced by $V_t$ cannot be described in the contract between the parties, since \Cref{eq:self_financing} depends via the security gain processes on the valuation adjustment $\psi_t^i$, which is specific of the investor pricing the strategy. Thus, the TVS defined in the contract will be
\begin{equation}
    d\bar{I}_t \coloneqq q_t \cdot \left(d\bar{S}_t + \frac{d\pi_t}{B_t} \right) - \bar{I}_t\phi_t dt \quad \text{with }I_0 = V_0, 
\label{eq:TVS_first}\end{equation}
leading to the following price process dynamics
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt -q_t\cdot \psi_t +dM_t^I,
\end{equation}
with $M_t^I$ martingale under $\mathbb{Q}$. In this case we observe that $I_t$ depends explicitly both on the valuation adjustments and on the allocation strategy. Indeed, if we substitute the valuation adjustments with their explicit expression (\Cref{eq:XVA_equity}), we get
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt - q_t \cdot S_t \mu_t dt + dM_t^I,
\end{equation}
where we can see the dependency on cost of carry $\mu_t^i$.
\subsection{The Volatility Targeting Constraint}
In a typical TVS the fund manager selects a risky-asset portfolio with a specific time-dependent allocation strategy expressed by means of the vector of relative weights $\alpha_t$, along with a risk-free asset, which we can identify with the bank account $B_t$. Usually TVSs are total-return products; thus we are justified in assuming $\pi_t=0$. Thus we can write \Cref{eq:TVS_first} as given by
\begin{equation}
    \frac{dI_t}{I_t}= \omega_t \alpha_t \cdot \frac{dS_t}{S_t} + \left(1-\omega_t  \alpha_t \cdot \mathds{1} \right)\frac{dB_t}{B_t}- \phi_t dt,
\label{TVS_elegant}\end{equation}
where $\mathds{1}$ is a $n$-dimensional vector of ones and $\omega_t\in[0,1]$ is determined so that the strategy log-normal volatility is kept constant, namely
\begin{equation}
        \omega_t: \quad \mathrm{Var}_t[dI_t] = \bar{\sigma}^2I_t^2dt,
\end{equation}
where $\Bar{\sigma}$ is the target volatility value.

We assume a generic continuous semi-martingale dynamics under the risk-neutral measure for the underlying securities, so that we can write
In practice, this means that the fund manager will select a risky-portfolio choosing $\alpha_t$ equities from the universe where he can trade and after that his choices will be scaled by the automatic target volatility algorithm\footnote{We recall that the universe of assets where the manager can trade and the value of $\bar{\sigma}$ are written in the contract.} $\omega_t$.

@@

@@

Thus the derivative price is given by:
\begin{equation}
    V_{T_{k-1}}\left(X_{T_{k-1}}, I_{T_{k-1}}\right)=\mathbb{E}_{T_{k-1}}\left[D_{T_{k-1}}\left(T_{k}\right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}\left(\alpha_{T_{k-1}}\right)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right],
\label{recursion}\end{equation}
while the iteration starts from maturity date where the boundary condition is set equal to the payoff function:
\begin{equation}
    V_{T_m} = \Phi\left(I_{T_m}\right).
\end{equation}
\subsection{Black and Scholes Model}
In the Black and Scholes model with deterministic rates, we can work with empty $X_t$, since in this case the portfolio dynamics \eqref{eq:TVS_last} is Markovian, leading to an optimal strategy $\alpha_t^*$ which depends in principle only on $I_t$. As a consequence, the local drift can be written as
\begin{equation}
     \ell \left(t,K\right) = \bar{\sigma}   \frac{\mu\left(t\right) \cdot \alpha\left(t,K\right)}{\|\alpha\left(t,K\right) \cdot \nu\left(t\right)\|},  
\end{equation}
so that the optimization problem can be solved looking only at the Markovian projection without simulating all the Brownian motions $W_t$. Notice that we are indicating the dependency on time in parenthesis to highlight that in this formula all the quantities are deterministic function of time.

@@

\section{Reinforcement Learning}\label{sec:RL}
As we have seen previously the determination of the derivative price on the TVS requires to  solve a stochastic control problem with continuous actions. Among the available standard techniques, Reinforcement Learning (RL) represents a new efficient way to solve stochastic optimal control problems in high dimensions.

 Reinforcement Learning (RL) describes how an agent behaves in an environment so to maximize some notion of cumulative reward. The actions of the agent as a function of his observations of the environment are termed the agent policy.  In our case the policy is the asset allocation weights $\alpha$, while the rewards are the costs generated by hedging a derivative contract on the TVS. Once the agent is trained, and the optimal policy is selected, we can run a Monte Carlo simulation to calculate the option price on the TVS.

 We adopt as learning strategy the PPO algoritm developed in \cite{ppo} and \cite{gae}. We have

\cleardoublepage
\printbibliography
\end{document}

>>>>

\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[outer=3.5cm, marginparwidth=4.5cm]{geometry}
%\usepackage{marginnote}
\usepackage{amssymb,amsmath,amsthm,latexsym,amsfonts,amscd,dsfont,enumerate,bbm,mathabx}
\usepackage{graphicx,tikz}
\usepackage{draftwatermark}
\usepackage{enumerate} 
% \usepackage{listings}
% \usepackage{booktabs}
\usepackage{mathtools}
% \usepackage[gen]{eurosym}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
\usepackage{soul}
\usepackage{comment}

@@

\newcommand{\tr}[1]{{#1}^{\intercal}} %transpose
\DeclareMathOperator{\Tr}{Tr}
\let\oldnorm\norm   % <-- Store original \norm as \oldnorm
\let\norm\undefined % <-- "Undefine" \norm
\DeclarePairedDelimiter\norm{\lVert}{\rVert}

@@

\title{Reinforcement Learning for Options on Target Volatility Funds}

\author{
	Roberto Daluiso\thanks{Intesa Sanpaolo Milan, roberto.daluiso@intesasanpaolo.com}
	\and 
	Emanuele Nastasi\thanks{Marketz S.p.A., emanuele.nastasi@marketz.eu}
	\and Andrea Pallavicini\thanks{Imperial College London and Intesa Sanpaolo Milan, a.pallavicini@imperial.ac.uk} 
	\and
	Stefano Polo \thanks{Intesa Sanpaolo Milan, stefano.polo@intesasanpaolo.com}% indicates same as 2nd thanks
}

\date{
	First Version: March 2021. This Version: \today
}
\begin{document} % goes here

@@

\begin{abstract}
\noindent In recent years Reinforcement Learning (RL) techniques are gaining popularity in the field of quantitative finance since they are proving to be an efficient way to solve  high-dimensional optimal control problems. 
Our research project is devoted to apply RL to price derivative contracts on target volatility strategies (TVSs), portfolios of risky assets and a risk-free one dynamically rebalanced in order to keep the realized volatility of the portfolio on a certain level. The uncertainty in the TVS risky portfolio composition along with the difference in hedging costs for each component requires to solve a stochastic control problem to evaluate the option prices. The topic of hedging costs is a novelty never dealt in the TVS literature and we provide a formal description of the entire control problem. We tackle the problem by implementing a Reinforcement Learning algorithm to determine the optimal risky portfolio composition leading to the most conservative option price.  We investigate the problem for two models of the risky asset dynamics: time-dependent Black \& Scholes and Local Volatility. In the first case we prove the existence of an analytical solution of the problem; a result that we use as benchmark to perform a series of fine-tuning of the hyper-parameters of the RL algorithm. At the end we provide numerical results for the Local Volatility model, for which an \textit{a priori} solution is not available.
\end{abstract}

\smallskip
\noindent
\textbf{JEL classification codes:} C63, C45, C61, G11, G13.\\
\textbf{AMS classification codes:} 65C05, 91G20, 91G60.\\
\textbf{Keywords:} Reinforcement Learning, Hedging Costs, Funding Costs, Proximal Policy Optimization, Target Volatility, Asset Allocation. 
\newpage
\tableofcontents
\newpage
\pagestyle{myheadings} \markboth{}{{\footnotesize Daluiso, Pallavicini, Nastasi, Polo, Reinforcement Learning for Options on Target Volatility Funds}}
\section{Introduction}
In the recent years portfolio managers are exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such environment is given by target volatility strategies (TVSs) (also known as constant volatility targeting) which are able to preserve the portfolio at a predetermined level of volatility. A TVS is  a  portfolio  of  risky  assets  (typically  equities)  and  a  risk-free  asset dynamically re-balanced with the aim of maintaining the overall portfolio volatility level closed to some target value. This products were initially offered in the Asian markets, see for instance the reports of \textcite{Chew} and \textcite{XUE} which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \textcite{Morrison}.

In literature TVSs are tested to investigate their performances in term of realized returns, see for instance \textcite{Hocquard28} and \textcite{PERCHET}, and the soundness of the volatility targeting algorithm, as described in \textcite{Kim}. Moreover, in pricing literature derivative contracts on TVS are studied, see in particular \textcite{Di_Graziano}, \textcite{Grasselli}, and \textcite{Albeverio}.

@@

Valuation adjustments (XVAs) is a topic widely discussed in the literature. We refer to \textcite{Brigo} for a discussion. Since fund managers allocating TVS usually rely on Equity assets, here we use the results of \textcite{Gabrielli} which  analyze the valuation adjustments for equity products. We can write
\begin{equation}
    \psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du,
\label{eq:XVA_equity}\end{equation}
where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

@@

Yet, the strategy priced by $V_t$ cannot be described in the contract between the parties, since \Cref{eq:self_financing} depends via the security gain processes on the valuation adjustment $\psi_t^i$, which is specific of the investor pricing the strategy. Thus, the TVS defined in the contract will be
\begin{equation}
    d\bar{I}_t \coloneqq q_t \cdot \left(d\bar{S}_t + \frac{d\pi_t}{B_t} \right) - \bar{I}_t\phi_t dt \quad \text{with }I_0 = V_0, 
\label{eq:TVS_first}\end{equation}
leading to the following price process dynamics
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt -q_t\cdot \psi_t +dM_t^I,
\end{equation}
with $M_t^I$ martingale under $\mathbb{Q}$. In this case we observe that $I_t$ depends explicitly both on the valuation adjustments and on the allocation strategy. Indeed, if we substitute the valuation adjustments with their explicit expression (\Cref{eq:XVA_equity}), we get
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt - q_t \cdot S_t \mu_t dt + dM_t^I,
\end{equation}
where we can see the dependency on cost of carry $\mu_t^i$.
\subsection{The Volatility Targeting Constraint}
In a typical TVS the fund manager selects a risky-asset portfolio with a specific time-dependent allocation strategy expressed by means of the vector of relative weights $\alpha_t$, along with a risk-free asset, which we can identify with the bank account $B_t$. Usually TVSs are total-return products; thus we are justified in assuming $\pi_t=0$. Thus we can write \Cref{eq:TVS_first} as given by
\begin{equation}
    \frac{dI_t}{I_t}= \omega_t \alpha_t \cdot \frac{dS_t}{S_t} + \left(1-\omega_t  \alpha_t \cdot \mathds{1} \right)\frac{dB_t}{B_t}- \phi_t dt,
\label{TVS_elegant}\end{equation}
where $\mathds{1}$ is a $n$-dimensional vector of ones and $\omega_t\in[0,1]$ is determined so that the strategy log-normal volatility is kept constant, namely
\begin{equation}
        \omega_t: \quad \mathrm{Var}_t[dI_t] = \bar{\sigma}^2I_t^2dt,
\end{equation}
where $\Bar{\sigma}$ is the target volatility value.
In practice, this means that the fund manager will select a risky-portfolio choosing $\alpha_t$ equities from the universe where he can trade and after that his choices will be scaled by the automatic target volatility algorithm\footnote{We recall that the universe of assets where the manager can trade and the value of $\bar{\sigma}$ are written in the contract.} $\omega_t$.

@@

\label{eq:recursion}\end{equation}

@@

Thus the derivative price is given by:
\begin{equation}
    V_{T_{k-1}}\left(X_{T_{k-1}}, I_{T_{k-1}}\right)=\mathbb{E}_{T_{k-1}}\left[D_{T_{k-1}}\left(T_{k}\right) V_{T_{k}}\left(X_{T_{k}}, I_{T_{k}}\left(\alpha_{T_{k-1}}\right)\right) \mid X_{T_{k-1}}, I_{T_{k-1}}\right],
\label{eq:recursion2}\end{equation}
while the iteration starts from maturity date where the boundary condition is set equal to the payoff function:
\begin{equation}
    V_{T_m} = \Phi\left(I_{T_m}\right).
\end{equation}

\subsection{Black and Scholes Model}
In the Black and Scholes model with deterministic rates, we can work with empty $X_t$, since in this case the portfolio dynamics \eqref{eq:TVS_last} is Markovian, leading to an optimal strategy $\alpha_t^*$ which depends in principle only on $I_t$. As a consequence, the local drift can be written as
\begin{equation}
     \ell \left(t,K\right) = \bar{\sigma}   \frac{\mu\left(t\right) \cdot \alpha\left(t,K\right)}{\|\alpha\left(t,K\right) \cdot \nu\left(t\right)\|},  
\end{equation}
so that the optimization problem can be solved looking only at the Markovian projection without simulating all the Brownian motions $W_t$. Notice that we are indicating the dependency on time in parenthesis to highlight that in this formula all the quantities are deterministic function of time.

@@

\subsection{Hamilton-Jacobi-Bellman Equation for Target Volatility Options} 
In this section we want to provide to the reader a formal description of the dynamic problem associated to options on target volatility strategies by writing the Hamilton-Jacobi-Bellman equation for the derivative value. We prove that from this description it is available the same closed formula \eqref{eq:BS_optimal_strategy} for the time-dependent BS model derived from the Gy\"ongy.

In full generality we suppose that the risky securities follows a generic multidimensional diffusive process $X_t$ given by the following SDE
\begin{equation}
		dX_t = M(X_t)dt + \Sigma(X_t) \cdot dW_t.
\end{equation}
The TVS dynamics is given as follows 
\begin{equation}
	\frac{dI_t}{I_t} = \left(r_t(X_t) -  \frac{\bar{\sigma} \alpha_t}{\|\alpha_t \cdot \nu_t(X_t)\|}  \cdot \mu_t(X_t)    \right)dt +\frac{\bar{\sigma}\alpha_t }{\|\alpha_t \cdot \nu_t(X_t) \|} \cdot \nu_t(X_t) \cdot dW_t
\end{equation}
Given $X := X_t$ and $I := I_t$, we can write the HJB equation for $V := V(t,I,X)$ as follows
\begin{equation}
	\begin{aligned}
		\frac{\partial V}{\partial t} + \max_\alpha  \left\{   \left(r_t(X) - \bar{\sigma}\frac{\alpha \cdot \mu_t(X)}{\|\alpha \cdot \nu_t(X)\|}\right) I \frac{\partial V}{\partial I} + (\nabla_X V) \cdot M(X) + \frac{1}{2} \bar{\sigma}^2I^2 \frac{\partial^2V}{\partial I^2}  \right.\\ 
		\left. +\frac{1}{2}\Tr\left(\tr{\Sigma(X)}(H_XV)\Sigma(X)\right)  + (\nabla_{X,I}V) \cdot \Sigma(X) \cdot \left(I\bar{\sigma}\frac{\alpha \cdot \nu_t(X)}{\|\alpha \cdot \nu_t(X)\|}\right)\right\} = 0,
	\end{aligned}
\end{equation}
where $\Tr(A)$ is the trace operator of $A$, $\nabla_X V$ the gradient of $V$ w.r.t. $X$, $H_XV$ the Hessian matrix of $V$ w.r.t. $X$ and $\nabla_{X,I}V $ is the vector defined by:
\begin{equation}
	\nabla_{X,I} V= \tr{\left(\frac{\partial^2 V}{\partial X^1 \partial I},\dots, \frac{\partial^2 V}{\partial X^n \partial I} \right)}.
\end{equation}
We take out from the maximum operator all the elements that do not depend on the risky allocation strategy $\alpha$
\begin{equation}
	\begin{aligned}
		\frac{\partial V}{\partial t} +   r_t(X) I \frac{\partial V}{\partial I} + (\nabla_X V) \cdot M(X) + \frac{1}{2} \bar{\sigma}^2I^2 \frac{\partial^2V}{\partial I^2} + \frac{1}{2}\Tr\left(\tr{\Sigma(X)}(H_XV)\Sigma(X)\right)  \\ 
		+\max_\alpha  \left\{  -\frac{\partial V}{\partial I} I  \bar{\sigma}\frac{\alpha \cdot \mu_t(X)}{\|\alpha \cdot \nu_t(X)\|} + 
		(\nabla_{X,I}V) \cdot \Sigma(X) \cdot \left(I\bar{\sigma}\frac{\alpha \cdot \nu_t(X)}{\|\alpha \cdot \nu_t(X)\|}\right)\right\} = 0.
		\end{aligned}
\label{eq:HJB_general}\end{equation}
\Cref{eq:HJB_general} represent the Hamilton-Jacobi-Bellman equation describing the TVS dynamic problem for a generic dynamics of the risky securities underlying the portfolio.
In our work we have that\footnote{We use $\circ$ for the element-wise product between two vectors and between vector and matrix.} $X_t = S_t$, $M(X_t) \coloneqq (r_t\mathds{1} - \mu_t)\circ S_t$ and $\Sigma(X_t) = S_t \circ \nu_t$.

If we assume a time-dependent BS dynamics for the risky equities ($\mu_t$, $r_t$ and $\nu_t$ deterministic), then $V = V(t,I)$ and all the derivatives w.r.t $X$ are all zero. Thus the reduced HJB is
\begin{equation}
	\frac{\partial V}{\partial t} +  I r(t)\frac{\partial V}{\partial I}  + \frac{1}{2}\bar{\sigma}^2I^2\frac{\partial^2V}{\partial I^2} + \max_\alpha \left\{ -\frac{\partial V}{\partial I} I  \bar{\sigma}\frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t)\|}\right\} = 0,
\end{equation}
so that if the payoff is increasing in $I_T$ by homogeneity of the SDE we get that $V$ is increasing and so the solution is given by
\begin{equation}
 \alpha^*(t) = \argmin_\alpha \frac{\alpha \cdot \mu(t)}{\|\alpha \cdot \nu(t)\|}
	\end{equation}
which is the same result expressed in \cref{eq:BS_optimal_strategy}. If the payoff is decreasing in $I_T$ then the solution will be the argmax.

Conversely, if we deal with a LV model for the $S_t$-dynamics, then $\nu_t = \nu(t,S_t)$ and there are no apparent simplifications in \cref{eq:HJB_general} thus we are not able to derive a closed form solution as in BS. In fact in the LV dynamics we have in the maximum operator the first order term derived from the drift of $I_t$ (as in BS) and a second order term which takes into account the volatility's smile functions deriving from the $S_t$-dynamics.

\section{Reinforcement Learning}\label{sec:RL}
As we have discussed previously in the case of general payoffs or risky securities dynamics, one must resort to numerical approaches to solve the stochastic control problem. The standard approach could be to use classical techniques based on backwards recursion \eqref{eq:recursion}-\eqref{eq:recursion2}. However their performances may degrade as the dimension $n$ of the problem increases. In our contribution we adopt a novel technique that is gaining popularity in many scientific branches for solving stochastic optimal control problems: Reinforcement Learning.

Reinforcement Learning is a branch of Machine Learning (ML) which allows an artificial agent to interact with an environment through actions and observations in order to maximize total rewards to achieve specific goals. In RL the agent is not told which actions to take but instead it must discover by trial and error which are the behaviors yielding to the greatest reward by trying them several times. This aspect makes RL independent  from pre-collected data as other ML techniques. Because of its nature, RL has been successful in quantitative finance for solving control problems; among the most important RL applications in this field, we refer to \textcite{pioneerrlfinance} as the pioneers in studying self-taught reinforcement trading problems, while to \textcite{rlintroductionfinance} and \textcite{rlfinance} for hedging derivatives with RL under market frictions.

\begin{comment}
\section{Numerical Investigation}
Dire qui che abbiamo lavorato con l'implementazione di OpenAi

The actions of the agent as a function of its observations of the environment are termed the agent policy.  In our case the policy is the asset allocation weights $\alpha$, while the rewards are the costs generated by hedging a derivative contract on the TVS. Once the agent is trained, and the optimal policy is selected, we can run a Monte Carlo simulation to calculate the option price on the TVS.

 We adopt as learning strategy the PPO algoritm developed in \textcite{ppo} and \textcite{gae}. We have 
\end{comment}
\cleardoublepage
\printbibliography
\end{document}
